Generation of TypeScript Declaration Files from JavaScript Code

### 2020-08-21 programming-2021/main.tex
Update number in abstract. Remove limiations regarding undefined type

This work presents \texttt{dts-generate}, a tool that generates
TypeScript declaration files for JavaScript libraries uploaded to the \NPM{}
registry. It extracts code examples from the documentation written by
the developer, executes the library driven by the examples, gathers
run-time information, and generates a declaration file based on this
information. To evaluate the tool, 244 declaration files were generated and 82 were
compared with the corresponding declaration file provided on DefinitelyTyped. 72 files presented positive results, having no differences at all or differences that can be solved by modifying the code examples accordingly.

@@

// Manually added:
gh('git+https://githuuub.com/monkey/business.git', {});
gh('git+https://githuuub.com/monkey/business.git', {enterprise: true});
gh({url: 'git://github.com/monkey/business.git'});
gh('this is not a proper url');
gh({url: 'this is not a proper url'});
    \end{lstlisting}
    \caption{Code example for module \texttt{github-url-to-object}.}
    \end{subfigure}
  \caption{Manually expanded code example for \texttt{github-url-to-object} to match DefinitelyTyped declaration file. Literal interface in DefinitelyTyped gets replace by a declared interface. The \texttt{undefined} type is used instead of the optional type. Return types are not considered.}
  \label{fig:experiments-results-manually-completed-examples}
\end{figure}

>>>>

This work presents \texttt{dts-generate}, a tool that generates
TypeScript declaration files for JavaScript libraries uploaded to the \NPM{}
registry. It extracts code examples from the documentation written by
the developer, executes the library driven by the examples, gathers
run-time information, and generates a declaration file based on this
information. To evaluate the tool, 244 declaration files were generated and 82 were
compared with the corresponding declaration file provided on DefinitelyTyped. 52 files presented positive results, having no differences at all or differences that can be solved by modifying the code examples accordingly.

@@

// Manually added:
gh('git+https://githuuub.com/monkey/business.git', {});
gh('git+https://githuuub.com/monkey/business.git', {enterprise: true});
gh({url: 'git://github.com/monkey/business.git'});
gh('this is not a proper url');
gh({url: 'this is not a proper url'});
    \end{lstlisting}
    \caption{Code example for module \texttt{github-url-to-object}.}
    \end{subfigure}
  \caption{Manually expanded code example for \texttt{github-url-to-object} to match DefinitelyTyped declaration file. Literal interface in DefinitelyTyped gets replace by a declared interface. Return types are not considered.}
  \label{fig:experiments-results-manually-completed-examples}
\end{figure}
